At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families - Supporting Information

### 2019-12-09 manuscript/reply_to_referees_2.tex

			By considering each family separately, we do risk obtaining some significant results purely by chance. The standard technique for addressing this type of multiple hypothesis testing, the Bonferroni correction, tends to be over-zealous and lead to a failure to reject the null hypothesis even when a large number of significant results before the correction supports the alternative hypothesis~\citep{Moran2003}. To account for multiple testing while also allowing the number of families showing significant trends to carry some weight, we use the correlated Bonferroni test introduced in~\citet{Drezner2016} (\emph{Supporting information 6}).

@@

		\end{quotation}

		Lines 354-357 now read:

			 In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table~\ref{family_slopes_pp}; Fig.~\ref{within_family_regression}). If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Supporting information 6}).
